Efficient Handling of String-Number Conversion

### 2019-11-23 evaluation.tex
minor

We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. We use the GitHub version stated in the parenthesis, and because their performance are in general better than the corresponding release version. 
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.

>>>>

We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. Foe these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version. 
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.
